\documentclass{article}
\title{Literature Review}
\date{Summer 2019}
\author{Jill Alexander}

\begin{document}
\maketitle
\newpage

\section{The CAT Vehicle Testbed: A Simulator with Hardware in the Loop for Autonomous Vehicle Applictaions}
	\subsection{Summary}
	Overview of the functions and content of the CAT Vehicle Testbed, a research testbed that can be used to mimic the dynamics of a real vehicle in a simulation.
	\subsection{Notes}
	\begin{itemize}
	\item basic overview of what the testbed is
	\end{itemize}
	\newpage
	

\section{A Safe Autonomous Vehicle Trajectory Domain Specific Modeling Language for Non-expert Development}
	\subsection{Summary}
	A high-level language can be used by non-experts and others to control low-level functions in an autonomous vehicle. A domain-specific language was used to turn simple commands into safe driving sequences. This language was then used by 4th graders to create unique paths for the car to drive on.
	\subsection{Key Points}
	\begin{itemize}
	\item Development can become unattainable to most people if designs are focused on too low-level functions.
	\item Domain specific modeling languages can be used to constrain designers to a specific modeling language.
	\item Verification was built in to ensure that the vehicle was always safely programmed.
	\item A decorator plugin was used to create a better visual aid for the designers.
	\end{itemize}
	\subsection{Notes}
	\begin{itemize}
	\item has good example code for verification of driving behaviors
	\item talks about using a Decorator Plugin
	\end{itemize}
	\newpage

\section{}
	\subsection{Summary}
	\subsection{Notes}
	\begin{itemize}
	\end{itemize}
	\newpage

\end{document}